Informal explination of study ``Ecotype detection in (geometric) morphometric data''

### 2013-01-13 documents/faqs_intro.Rnw
faq draft

<<pca-plots, eval = FALSE>>=
gg.pca
@
\begin{figure}[p]
  \centering
  \includegraphics[height = 0.4\textheight, keepaspectratio = true]{figure/pca-plots5}
  \caption{Comparison of first four pricipal components of Procrustes fit landmarks. Familes are highlighted.}
  \label{fig:fish-pca}
\end{figure}

@@

% model selection table
<<fish-model-table, results = 'asis'>>=
print(ftab, 
      table.placement = 'p',
      caption.placement = 'bottom',
      sanitize.text.function = function(x) x,
      sanitize.colnames.function = function(x) x)
@

@@

<<logistic-plots, eval = FALSE>>=
gf
@
\begin{figure}[p]
  \centering
  \includegraphics[width = 0.4\textwidth, keepaspectratio = true]{figure/logistic-plots}
  \caption{Relative probabilities of Characiform family identification from the first two principal components of shape. The first two pricipal components are plotted here because they are the predictors of family from the AICc-best model.}
  \label{fig:fish-logistic}
\end{figure}

>>>>

<<pca-plots, eval = FALSE>>=
gg.pca
@
\begin{figure}[p]
  \centering
  \includegraphics[width= \textwidth, keepaspectratio = true]{figure/pca-plots5}
  \caption{Comparison of first four pricipal components of Procrustes fit landmarks. Familes are highlighted.}
  \label{fig:fish-pca}
\end{figure}

@@

% model selection table
<<fish-model-table, results = 'asis'>>=
print(ftab, 
      table.placement = 'p',
      caption.placement = 'bottom',
      sanitize.text.function = function(x) x,
      sanitize.colnames.function = function(x) x,
      scalebox = 0.7)
@

@@

<<logistic-plots, eval = FALSE>>=
gf
@
\begin{figure}[p]
  \centering
  \includegraphics[height = 0.5\textheight, keepaspectratio = true]{figure/logistic-plots}
  \caption{Relative probabilities of Characiform family identification from the first two principal components of shape. The first two pricipal components are plotted here because they are the predictors of family from the AICc-best model.}
  \label{fig:fish-logistic}
\end{figure}

### 2013-01-13 documents/faqs_intro.tex
faq draft

\begin{knitrout}
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/pca-plots}

\end{knitrout}

\begin{figure}[p]
  \centering
  \includegraphics[height = 0.4\textheight, keepaspectratio = true]{figure/pca-plots3}
  \caption{Comparison of first four pricipal components of Procrustes fit landmarks. Familes are highlighted.}
  \label{fig:fish-pca}
\end{figure}

@@

% model selection table
% latex table generated in R 2.15.2 by xtable 1.7-0 package
% Fri Jan 11 16:26:20 2013
\begin{table}[p]
\begin{center}
\begin{tabular}{rlllllllllrrrrr}
  \hline
 & (Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & family & df & logLik & AICc & delta & weight \\ 
  \hline
2 & + & + & + &  &  &  &  &  &  & 9.00 & -14.34 & 50.35 & 0.00 & 0.97 \\ 
  3 & + & + & + & + &  &  &  &  &  & 12.00 & -13.18 & 57.15 & 6.80 & 0.03 \\ 
  4 & + & + & + & + & + &  &  &  &  & 15.00 & -11.46 & 64.09 & 13.74 & 0.00 \\ 
  5 & + & + & + & + & + & + &  &  &  & 18.00 & -8.82 & 70.73 & 20.39 & 0.00 \\ 
  1 & + & + &  &  &  &  &  &  &  & 6.00 & -33.71 & 81.03 & 30.68 & 0.00 \\ 
  6 & + & + & + & + & + & + & + &  &  & 21.00 & -7.10 & 81.17 & 30.82 & 0.00 \\ 
  7 & + & + & + & + & + & + & + & + &  & 24.00 & -0.04 & 83.38 & 33.04 & 0.00 \\ 
   \hline
\end{tabular}
\caption{Model selection table.}
\label{tab:fish-tab}
\end{center}
\end{table}

% latex table generated in R 2.15.2 by xtable 1.7-0 package
% Fri Jan 11 16:26:20 2013
\begin{table}[p]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & ano & chi & cur & pro \\ 
  \hline
ano &   4 &   0 &   0 &   0 \\ 
  chi &   0 &   1 &   0 &   0 \\ 
  cur &   0 &   0 &  12 &   0 \\ 
  pro &   0 &   0 &   0 &   2 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix.}
\label{tab:fish-mod}
\end{center}
\end{table}

\begin{figure}[p]
  \centering
  \includegraphics[width = 0.4\textwidth, keepaspectratio = true]{figure/logistic-plots}
  \caption{Relative probabilities of Characiform family identification from the first two principal components of shape. The first two pricipal components are plotted here because they are the predictors of family from the AICc-best model.}
  \label{fig:fish-logistic}
\end{figure}

>>>>

\begin{figure}[p]
  \centering
  \includegraphics[width= \textwidth, keepaspectratio = true]{figure/pca-plots5}
  \caption{Comparison of first four pricipal components of Procrustes fit landmarks. Familes are highlighted.}
  \label{fig:fish-pca}
\end{figure}

@@

% model selection table
% latex table generated in R 2.15.2 by xtable 1.7-0 package
% Sat Jan 12 13:35:24 2013
\begin{table}[p]
\begin{center}
\scalebox{0.7}{
\begin{tabular}{rlllllllllrrrrr}
  \hline
 & (Intercept) & PC1 & PC2 & PC3 & PC4 & PC5 & PC6 & PC7 & family & df & logLik & AICc & delta & weight \\ 
  \hline
2 & + & + & + &  &  &  &  &  &  & 9.00 & -14.34 & 50.35 & 0.00 & 0.97 \\ 
  3 & + & + & + & + &  &  &  &  &  & 12.00 & -13.18 & 57.15 & 6.80 & 0.03 \\ 
  4 & + & + & + & + & + &  &  &  &  & 15.00 & -11.46 & 64.09 & 13.74 & 0.00 \\ 
  5 & + & + & + & + & + & + &  &  &  & 18.00 & -8.82 & 70.73 & 20.39 & 0.00 \\ 
  1 & + & + &  &  &  &  &  &  &  & 6.00 & -33.71 & 81.03 & 30.68 & 0.00 \\ 
  6 & + & + & + & + & + & + & + &  &  & 21.00 & -7.10 & 81.17 & 30.82 & 0.00 \\ 
  7 & + & + & + & + & + & + & + & + &  & 24.00 & -0.04 & 83.38 & 33.04 & 0.00 \\ 
   \hline
\end{tabular}
}
\caption{Model selection table.}
\label{tab:fish-tab}
\end{center}
\end{table}

% latex table generated in R 2.15.2 by xtable 1.7-0 package
% Sat Jan 12 13:35:24 2013
\begin{table}[p]
\begin{center}
\begin{tabular}{rrrrr}
  \hline
 & ano & chi & cur & pro \\ 
  \hline
ano &   4 &   0 &   0 &   0 \\ 
  chi &   0 &   1 &   0 &   0 \\ 
  cur &   0 &   0 &  12 &   0 \\ 
  pro &   0 &   0 &   0 &   2 \\ 
   \hline
\end{tabular}
\caption{Confusion matrix.}
\label{tab:fish-mod}
\end{center}
\end{table}

\begin{figure}[p]
  \centering
  \includegraphics[height = 0.5\textheight, keepaspectratio = true]{figure/logistic-plots}
  \caption{Relative probabilities of Characiform family identification from the first two principal components of shape. The first two pricipal components are plotted here because they are the predictors of family from the AICc-best model.}
  \label{fig:fish-logistic}
\end{figure}
